Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-06-04 main.tex
More references

There are several previous publications that use evolutionary algorithms to
evolve IPD strategies in various circumstances \cite{fogel1993evolving} \cite{ashlock2006training}
\cite{ashlock2006changes} \cite{vassiliades2010multiagent} \cite{ashlock2014shaped}
\cite{ashlock2014evolution} \cite{ashlock2015multiple} \cite{barlow2015varying}
\cite{sudo2015effects}. See also \cite{gaudesi2016exploiting} for a strategy trained to win against
a collection of well-known IPD opponents. Our results are unique in that we are
able to train against a large collection of well-known strategies available in
the scientific literature.

>>>>

There are several previous publications that use evolutionary algorithms to
evolve IPD strategies in various circumstances \cite{marks1989niche} \cite{fogel1993evolving} \cite{ashlock2006training}
\cite{ashlock2006changes} \cite{vassiliades2010multiagent} \cite{ashlock2014shaped}
\cite{ashlock2014evolution} \cite{ashlock2015multiple} \cite{barlow2015varying}
\cite{sudo2015effects}. See also \cite{gaudesi2016exploiting} for a strategy
trained to win against a collection of well-known IPD opponents and see
\cite{franken2005particle} for a prior use of particle swarm algorithms. Our
results are unique in that we are able to train against a large collection of
well-known strategies available in the scientific literature.
